### 2015-02-20 fundamentals/impl.tex
simplifying language in implementation

Groundbreaking insights and new classes of problems can be investigated by
leveraging modern massive computing resources.
However, many fuel cycle simulators rely on \gls{COTS} and Windows-only software that limits
performance on and compatibility with resource computing infrastructures. This limitation severely
limits the possible scope of simulations and increases the wall-clock time necessary to conduct parameterized sensitivity
analyses and other multi-simulation studies. \Cyclus, on the other hand, is
primarily written in \texttt{C++} and relies on
libraries supported by Linux and UNIX (including Ubuntu and OSX) platforms,
which are flexible and support parallelization.
Furthermore, the core infrastructure and related archetypes are free and
open source, BSD-3-clause licensed. No part of \Cyclus is proprietary or based
on \gls{COTS}, Windows-only software. \Cyclus can therefore be easily deployed
on large computer systems, such as \gls{HTC} systems.

@@

The \Cyclus architecture encourages efficient, targeted contribution to the ecosystem of
archetype libraries.
With \Cyclus, a researcher can focus on generating an archetype model within their
sphere of expertise, while relying on the contributions of others to fill
in the other technologies in the simulation.
Similarly, individual developers may explore different levels of complexity within their archetypes, including
wrapping other simulation tools as loadable libraries within \Cyclus.

\Cyclus acheives this behavior by implementing its generic \gls{API} and
modular architecture via a suite of dynamically loadable plug-in libraries.
Though common in modern software architecture, such a plug-in pattern has not
previously been implemented in nuclear fuel cycle simulators.  Dynamically
loadable libraries are the primary mechanism for extending \Cyclus' capability.
This approach provides encapsulation: the core framework operates
independently from the individual plug-in libraries. Thus, any customization or
extension is implemented only in the loadable library.

@@

This last benefit of dynamically loadable libraries addresses
another goal of \Cyclus: ubiquity amongst its potential user base. By
engineering \Cyclus to easily handle varying levels of complexity, a single
simulation engine can be used by both users interested in big-picture policy
questions as well as users focused on more detailed, technical
analyses. They merely choose their preferred level of fidelity from the
available libraries.

@@

\Cyclus implements an \acrlong{ABM} paradigm.  \gls{ABM} is modern, sophisticated,
true to reality, and incorporates modern computing resources.
Furthermore, \gls{ABM} provides a natural
perspective from which to model a given problem. In the nuclear fuel cycle
context, for example, an analyst can design an agent with reactor-related logic
that is entirely independent from an agent with fuel fabrication-related
logic. Defining the behavior of both agents according to the
\gls{API} contract is sufficient for them to interact with one another as
bona fide actors in the simulation.  The two archetype libraries can be used in the same
simulation without any shared knowledge.

>>>>

Groundbreaking insights and new classes of problems can be investigated by
leveraging modern massive computing resources.
However, many fuel cycle simulators rely on \gls{COTS} and Windows-only software that limits
performance on and compatibility with resource computing infrastructures. This
severely constrains the possible scope of simulations and increases the wall-clock time necessary to conduct parameterized sensitivity
analyses and other multi-simulation studies. \Cyclus, on the other hand, is
primarily written in \texttt{C++} and relies on
libraries supported by Linux and UNIX (including Ubuntu and OSX) platforms,
which are flexible and support parallelization.
Furthermore, the core infrastructure and related archetypes are free and
open source, BSD-3-clause licensed. No part of \Cyclus is proprietary or based
on \gls{COTS}, Windows-only software. \Cyclus can therefore be easily deployed
on large computer systems, such as \gls{HTC} systems.

@@

The \Cyclus architecture encourages efficient, targeted contribution to the ecosystem of
archetype libraries.
With \Cyclus, a researcher can focus on generating an archetype model within their
sphere of expertise while relying on the contributions of others to fill
in the other technologies in the simulation.
Similarly, individual developers may explore different levels of complexity within their archetypes, including
wrapping other simulation tools as loadable libraries within \Cyclus.

\Cyclus acheives this behavior by implementing its generic \gls{API} and
modular architecture via a suite of dynamically loadable plug-in libraries, as
pictured in Figure \ref{fig:framework}.
Though common in modern software architecture, such a plug-in pattern has not
previously been implemented in a nuclear fuel cycle simulator. Dynamically
loadable libraries are the primary mechanism for extending \Cyclus' capability.
This approach provides encapsulation: the core framework operates
independently from the individual plug-in libraries. Thus, any customization or
extension is implemented only in the loadable library.

@@

This last benefit of dynamically loadable libraries addresses
another goal of \Cyclus: ubiquity amongst its potential user base. By
engineering \Cyclus to easily handle varying levels of complexity, a single
simulation engine can be used by both users interested in big-picture policy
questions as well as users focused on more detailed, technical
analyses. They merely choose their preferred level of fidelity from among the
available libraries in the ecosystem.

@@

\Cyclus implements an \acrlong{ABM} paradigm.  \gls{ABM} is modern, sophisticated,
true to reality, and incorporates modern computing resources.
Furthermore, \gls{ABM} provides a natural
perspective from which to model a given problem. In the nuclear fuel cycle
context, for example, an analyst can design a reactor agent
that is entirely independent from a fuel fabrication agent. Defining the behavior of both agents according to the
\gls{API} contract is sufficient for them to interact with one another as
bona fide actors in the simulation.  The two archetype libraries can be used in the same
simulation without any shared knowledge.
